WEO against OECD - CPI

### 2023-08-22 oecd_data/weo_oecd_check_cpi.Rmd
check cpi values after changing data source

```{r oecd, warning = FALSE}
oecd <- read.csv(here("oecd_data", "oecd_cpi.csv"))

oecd_q <- oecd |> 
  filter(FREQUENCY == "Q",
         SUBJECT == "TOT") |>
  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
  rename(country = LOCATION,
         measure = MEASURE,
         yrq = TIME,
         value = Value) |>
  mutate(target_year = substr(yrq, 1, 4) |> as.numeric(),
         quarter = substr(yrq, 7, 7) |> as.numeric()) |>
  filter(target_year >= 1989,
         quarter == 4,
         measure == "AGRWTH") |>
  select(-c(yrq, quarter)) |>
  rename(q4val = value,
         ccode = country) |>
  select(-measure)

oecd_y <- oecd |> 
  filter(FREQUENCY == "A",
         SUBJECT == "TOT") |>
  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA"),
         MEASURE == "AGRWTH") |>
  select(-c(INDICATOR, SUBJECT, FREQUENCY, Flag.Codes)) |>
  rename(country = LOCATION,
         measure = MEASURE,
         target_year = TIME,
         value = Value) |>
  mutate(target_year = as.numeric(target_year)) |>
  filter(target_year >= 1990) |>
  group_by(country) |>
  arrange(target_year,  .by_group = TRUE) |>
  rename(yearval = value,
         ccode = country) |>
  select(-measure)

@@

weodat_g7 <- weodat |>
  filter(horizon == 0.5,
         !is.na(tv_1),
         g7 == "G7",
         target == "pcpi_pch") |>
  rename(ccode = ISOAlpha_3Code) |>
  select(ccode, country, target_year, tv_1, tv_2) |>
  distinct() |>
  left_join(oecd_y, by = c("ccode", "target_year")) |>
  left_join(oecd_q, by = c("ccode", "target_year")) |>
  setDT() |>
  melt(id.vars = c("ccode", "country", "target_year"), 
       variable.name = "truth_type", 
       value.name = "truth_value") |>
  filter(truth_type != "q4val") |>
  mutate(truth_type = factor(truth_type, 
                             levels = c("tv_1", "tv_2", "yearval", "q4val"),
                             labels = c("WEO_1yr", "WEO_2yr", "OECD_annual", "OECD_q4q4")))

>>>>

```{r oecd, warning = FALSE}
oecd <- read.csv(here("oecd_data", "oecd_cpi_quarter.csv"))

oecd_y <- read.csv(here("oecd_data", "oecd_cpi_quarter.csv")) |>
  filter(Subject == "CPI: 01-12 - All items",
         MEASURE %in% c("GP")) |>
  select(-c(Measure, SUBJECT, Subject)) |>
  select(LOCATION, MEASURE, TIME, Unit, Value) |>
  rename(ccode = LOCATION,
         measure = MEASURE,
         yrq = TIME,
         value = Value) |>
  mutate(target_year = substr(yrq, 1, 4) |> as.numeric(),
         quarter = substr(yrq, 7, 7) |> as.numeric()) |>
  mutate(quarter = ifelse(is.na(quarter), "Y", quarter)) |>
  select(-yrq) |>
  filter(ccode %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "GBR", "USA")) |>
  filter(quarter == "Y") |>
  select(-quarter) |>
  rename(yearval = value)

@@

weodat_g7 <- weodat |>
  filter(horizon == 0.5,
         !is.na(tv_1),
         g7 == 1,
         target == "pcpi_pch") |>
  rename(ccode = ISOAlpha_3Code) |>
  select(ccode, country, target_year, tv_1, tv_2) |>
  distinct() |>
  left_join(oecd_y, by = c("ccode", "target_year")) |>
  #left_join(oecd_q, by = c("ccode", "target_year")) |>
  setDT() |>
  select(c(ccode, country, target_year, tv_1, tv_2, yearval)) |>
  melt(id.vars = c("ccode", "country", "target_year"), 
       variable.name = "truth_type", 
       value.name = "truth_value") |>
  filter(truth_type != "q4val") |>
  mutate(truth_type = factor(truth_type, 
                             levels = c("tv_1", "tv_2", "yearval", "q4val"),
                             labels = c("WEO_1yr", "WEO_2yr", "OECD_annual", "OECD_q4q4")))
